---
title: "Getting recent co-authors from Pubmed"
author: "Tim Read"
date: "January 21, 2015"
output:
  html_document: default
---

Trying to solve the problem of generating a non-redundant list of recent coathors for a NSF application COI list.  Inspired by this [blogpost from Dave Tang: ](http://davetang.org/muse/2013/10/31/querying-pubmed-using-r/).

####First, open the libraries and load the query (boring)####
```{r, echo = FALSE}
library("RISmed")
library("dplyr")
res <- EUtilsSummary('read td', type='esearch', db='pubmed', mindate='2013', maxdate='2015')
fetch <- EUtilsGet(res)
```

####Now use a for-loop to iteratively merge the first two columns####

```{r}
a_list = NULL
for (i in 1:length(Author(fetch))){
  if (i == 1) {a_list <- Author(fetch)[[1]][,1:2]}
  else {
    a_list <- dplyr::union(a_list,Author(fetch)[[i]][,1:2])
  }
}

print(a_list)
```
Not bad: **106 co-authors** in the last two years!.


####Now I want a plot of all the mentions of my favourite word 'plasmid'####
```{r}
#first how many total articles containing plasmid
res3 <- EUtilsSummary('plasmid', type='esearch', db='pubmed')
 
summary(res3)

tally <- array()
x <- 1
for (i in 1970:2013){
  Sys.sleep(1)
  r <- EUtilsSummary('plasmid', type='esearch', db='pubmed', mindate=i, maxdate=i)
  tally[x] <- QueryCount(r)
  x <- x + 1
}
names(tally) <- 1970:2013
max(tally)

barplot(tally, las=2, ylim=c(0,max(tally)), main="Number of PubMed articles containing plasmid")

```



####Session info####
```{r}
sessionInfo()
```


